---
title: "Appendix 2. Visualization"
output: html_notebook
---
# Load necessary libraries
```{r}
df_score <- read.csv("LIWC_scoresOnly.csv", 
                    header = TRUE, stringsAsFactors = FALSE)

print(df_score)
```
# Load necessary libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# package to reorder factors
library(forcats)

# position labels near the points without overlap
library(ggrepel)
```

# Convert df_score to long format, excluding 'Segment' and 'WC'
```{r}
df_long <- df_score %>%
  
  # exclude 'Segment' and 'WC(wordcount)' columns
  select(-Segment, -WC) %>% 
  
  # transform all columns except 'Type' into long format
  pivot_longer(cols = -Type, 
               names_to = "Dictionary",
               values_to = "Score")

print(head(df_long))
```

# Reflections on confusing parts 

# Calculate the differences among groups and filter out dictionaries with low scores 
```{r}
confusing_vis <- df_long %>%
  filter(Type %in% c('A_group_Confusing', 'B_group_Confusing', 
                     'C_group_Confusing')) %>%
  group_by(Dictionary, Type) %>%
  summarize(mean = mean(Score), 
            se = sd(Score) / sqrt(n()), 
            N = n(), 
            .groups = "drop") %>%
  
  # reshape a dataset from long format to wide format
  # 'Type' will be columns
  pivot_wider(names_from = Type, values_from = mean) %>%
  
  # add filtering step to drop dictionaries where all scores are below 10
 filter(`A_group_Confusing` >= 10 | `B_group_Confusing` >= 10 | 
          `C_group_Confusing` >= 10) %>%
  
  # calculate the difference among three groups (variance)
  mutate(diff = abs(`A_group_Confusing` - `B_group_Confusing`) +
                abs(`C_group_Confusing` - `C_group_Confusing`) +
                abs(`B_group_Confusing` - `C_group_Confusing`)) %>%
  
  # sort by the largest difference first
  arrange(desc(diff))  
```



# Reorder the Dictionary terms based on the difference
```{r}
confusing_vis <- confusing_vis %>%
  
  # make the datafraeme long again
  pivot_longer(cols = c(`A_group_Confusing`, `B_group_Confusing`, `C_group_Confusing`),
               names_to = "Type", values_to = "mean") %>%
  
  # and then reorder based on the between-group variances
  mutate(Dictionary = fct_reorder(Dictionary, diff, .desc = TRUE))  
```

# Plot the reordered data

```{r}

# Visualization using ggplot
p_confusing <- confusing_vis %>%
  
  # `fill` sets bar colors by group
  ggplot(aes(x = Dictionary, y = mean, color = Type)) +
  
  # use `geom_point` for dot plot, `position = "dodge"` for side-by-side bars
  geom_point(position = position_dodge(width = 0.5), size = 2, alpha = 1) +   
  
  # color the bars based on the groups
  scale_color_manual(name = "Group", 
                   values = c("A_group_Confusing" = "#FF6347",
                              "B_group_Confusing" = "#4682B4",
                              "C_group_Confusing" = "#32CD32"),
                   labels = c("Group A", "Group B", "Group C")) +
  
  # add numbers on the top of each bar
  geom_text_repel(aes(label = round(mean, 1)), 
                  position = position_dodge(width = 0.8),  
                  size = 2.5,
                  alpha = 1) + 
  
  # black and white theme
  theme_bw(base_size = 16) +
  
  # customize axis and label
  labs(x = "Dictionaries of LIWC-22", y = "Score (%)",
       title = "LIWC Analysis of Student Reflections on Confusing Parts") +
    
  theme(axis.text.x = element_text(angle = 70, hjust = 1, size = 8),
        
        # adjust the title font size
        plot.title = element_text(size = 14),
        
        # adjust x,y-axis label font size
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))


p_confusing
```

# Reflections on interesting parts 

# Calculate the differences among groups and filter out dictionaries with low scores 
```{r}
interesting_vis <- df_long %>%
  filter(Type %in% c('A_group_Interesting', 'B_group_Interesting', 'C_group_Interesting')) %>%
  group_by(Dictionary, Type) %>%
  summarize(mean = mean(Score), 
            se = sd(Score) / sqrt(n()), 
            N = n(), 
            .groups = "drop") %>%
  
  # reshape a dataset from long format to wide format
  # 'Type' will be columns
  pivot_wider(names_from = Type, values_from = mean) %>%
  
  # add filtering step to drop dictionaries where all scores are below 10
 filter(`A_group_Interesting` >= 10 | `B_group_Interesting` >= 10 | 
          `C_group_Interesting` >= 10) %>%
  
  # calculate the difference among three groups (variance)
  mutate(diff = abs(`A_group_Interesting` - `B_group_Interesting`) +
                abs(`A_group_Interesting` - `C_group_Interesting`) +
                abs(`B_group_Interesting` - `C_group_Interesting`)) %>%
  
  # sort by the largest difference first
  arrange(desc(diff))  
```



# Reorder the Dictionary terms based on the difference
```{r}
interesting_vis <- interesting_vis %>%
  
  # make the datafraeme long again
  pivot_longer(cols = c(`A_group_Interesting`, `B_group_Interesting`, 
                        `C_group_Interesting`),
               names_to = "Type", values_to = "mean") %>%
  
  # and then reorder based on the between-group variances
  mutate(Dictionary = fct_reorder(Dictionary, diff, .desc = TRUE))  
```


# Plot the reordered data
```{r}

# Visualization using ggplot
p_interesting <- interesting_vis %>%
  
  # `fill` sets bar colors by group
  ggplot(aes(x = Dictionary, y = mean, color = Type)) +
  
  # use `geom_point` for dot plot, `position = "dodge"` for side-by-side bars
  geom_point(position = position_dodge(width = 0.5), size = 2, alpha = 1) +   
  
  # color the bars based on the groups
  scale_color_manual(name = "Group", 
                   values = c("A_group_Interesting" = "#FF6347",
                              "B_group_Interesting" = "#4682B4",
                              "C_group_Interesting" = "#32CD32"),
                   labels = c("Group A", "Group B", "Group C")) +
  
  # add numbers on the top of each bar
  geom_text_repel(aes(label = round(mean, 1)), 
                  position = position_dodge(width = 0.8),  
                  size = 2.5,
                  alpha = 1) + 
  
  # black and white theme
  theme_bw(base_size = 16) +
  
  # customize axis and label
  labs(x = "Dictionaries of LIWC-22", y = "Score (%)",
       title = "LIWC Analysis of Student Reflections on Interesting Parts",
       fontsize = 8) +
    
  theme(axis.text.x = element_text(angle = 70, hjust = 1, size = 8),
        plot.title = element_text(size = 14),  # Adjust the title font size
        axis.title.x = element_text(size = 12),  # Adjust x-axis label font size
        axis.title.y = element_text(size = 12))


p_interesting

```



