---
title: "Final_Visualization"
output: html_notebook
---
# Load necessary libraries
```{r}
df_score <- read.csv("LIWC_scoresOnly.csv", 
                    header = TRUE, stringsAsFactors = FALSE)

print(df_score)
```
# Load necessary libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# package to reorder factors
library(forcats) 
```


# Convert df_score to long format, excluding 'Segment' and 'WC'
```{r}
df_long <- df_score %>%
  
  # exclude 'Segment' and 'WC(wordcount)' columns
  select(-Segment, -WC) %>% 
  
  # transform all columns except 'Type' into long format
  pivot_longer(cols = -Type, 
               names_to = "Dictionary",
               values_to = "Score")

print(head(df_long))
```

# Reflections on confusing parts 

# Calculate the differences among groups and filter out dictionaries with low scores 
```{r}
confusing_vis <- df_long %>%
  filter(Type %in% c('Confusing (A Group)', 'Confusing (B Group)', 
                     'Confusing (C Group)')) %>%
  group_by(Dictionary, Type) %>%
  summarize(mean = mean(Score), 
            se = sd(Score) / sqrt(n()), 
            N = n(), 
            .groups = "drop") %>%
  
  # reshape a dataset from long format to wide format
  # 'Type' will be columns
  pivot_wider(names_from = Type, values_from = mean) %>%
  
  # add filtering step to drop dictionaries where all scores are below 10
 filter(`Confusing (A Group)` >= 20 | `Confusing (B Group)` >= 20 | 
          `Confusing (C Group)` >= 20) %>%
  
  # calculate the difference among three groups (variance)
  mutate(diff = abs(`Confusing (A Group)` - `Confusing (B Group)`) +
                abs(`Confusing (A Group)` - `Confusing (C Group)`) +
                abs(`Confusing (B Group)` - `Confusing (C Group)`)) %>%
  
  # sort by the largest difference first
  arrange(desc(diff))  
```



# Reorder the Dictionary terms based on the difference
```{r}
confusing_vis <- confusing_vis %>%
  
  # make the datafraeme long again
  pivot_longer(cols = c(`Confusing (A Group)`, `Confusing (B Group)`, `Confusing (C Group)`),
               names_to = "Type", values_to = "mean") %>%
  
  # and then reorder based on the between-group variances
  mutate(Dictionary = fct_reorder(Dictionary, diff, .desc = TRUE))  
```

# Create two filtered datasets, one for scores under 50 and one for scores under 100
```{r}
confusing_vis_under_50 <- confusing_vis %>%
  filter(mean < 50)

confusing_vis_under_100 <- confusing_vis %>%
  filter(mean < 100)
```

# Plot for scores under 50
```{r}
p_confusing_under_50 <- confusing_vis_under_50 %>%
  
  # `fill` sets bar colors by group
  ggplot(aes(x = Dictionary, y = mean, fill = Type)) +
  
  # use `geom_col` for bar graph, `position = "dodge"` for side-by-side bars
  geom_col(position = "dodge", width = 0.7) +  
  
  scale_fill_manual(name = "Group", 
                    values = c("Confusing (A Group)" = "red", 
                               "Confusing (B Group)" = "blue", 
                               "Confusing (C Group)" = "green")) +
  
  # black and white theme
  theme_bw(base_size = 16) +
  
  # customize axis and label
  labs(x = "Confusing Categories", y = "Score") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1, size = 8))

print(p_confusing_un)
```



# Plot for scores under 100
```{r}
p_confusing_under_100 <- confusing_vis_under_100 %>%
  ggplot(aes(x = Dictionary, y = mean, color = Type)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +  # Add points for each group
  geom_errorbar(aes(ymin = mean - 2 * se, ymax = mean + 2 * se), width = 0.2, position = position_dodge(0.5)) +  # Scale up the error bars
  scale_color_manual(name = "Group", values = c("Confusing (A Group)" = "red", "Confusing (B Group)" = "blue", "Confusing (C Group)" = "green")) +
  theme_bw(base_size = 16) +
  labs(x = "Confusing Categories (Scores under 100)", y = "Score") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1, size = 8))

print(p_confusing_under_100)
```


# Plot the all reordered data

```{r}
p_confusing <- confusing_vis %>%
  
  # `fill` sets bar colors by group
  ggplot(aes(x = Dictionary, y = mean, fill = Type)) +
  
  # use `geom_col` for bar graph, `position = "dodge"` for side-by-side bars
  geom_col(position = "dodge", width = 0.7) +  
  
  scale_fill_manual(name = "Group", 
                    values = c("Confusing (A Group)" = "red", 
                               "Confusing (B Group)" = "blue", 
                               "Confusing (C Group)" = "green")) +
  
  # black and white theme
  theme_bw(base_size = 16) +
  
  # customize axis and label
  labs(x = "Confusing Categories", y = "Score") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1, size = 8))

print(p_confusing)
```

# Reflections on interesting parts 

# Calculate the differences among groups and filter out dictionaries with low scores 
```{r}
interesting_vis <- df_long %>%
  filter(Type %in% c('Interesting (A Group)', 'Interesting (B Group)', 'Interesting (C Group)')) %>%
  group_by(Dictionary, Type) %>%
  summarize(mean = mean(Score), 
            se = sd(Score) / sqrt(n()), 
            N = n(), 
            .groups = "drop") %>%
  
  # reshape a dataset from long format to wide format
  # 'Type' will be columns
  pivot_wider(names_from = Type, values_from = mean) %>%
  
  # add filtering step to drop dictionaries where all scores are below 20
 filter(`Interesting (A Group)` >= 20 | `Interesting (B Group)` >= 20 | 
          `Interesting (C Group)` >= 20) %>%
  
  # calculate the difference among three groups (variance)
  mutate(diff = abs(`Interesting (A Group)` - `Interesting (B Group)`) +
                abs(`Interesting (A Group)` - `Interesting (C Group)`) +
                abs(`Interesting (B Group)` - `Interesting (C Group)`)) %>%
  
  # sort by the largest difference first
  arrange(desc(diff))  
```



# Reorder the Dictionary terms based on the difference
```{r}
interesting_vis <- interesting_vis %>%
  
  # make the datafraeme long again
  pivot_longer(cols = c(`Interesting (A Group)`, `Interesting (B Group)`, 
                        `Interesting (C Group)`),
               names_to = "Type", values_to = "mean") %>%
  
  # and then reorder based on the between-group variances
  mutate(Dictionary = fct_reorder(Dictionary, diff, .desc = TRUE))  
```


# Plot the reordered data
```{r}
p_interesting <- interesting_vis %>%
  
  # `fill` sets bar colors by group
  ggplot(aes(x = Dictionary, y = mean, fill = Type)) +
  
  # use `geom_col` for bar graph, `position = "dodge"` for side-by-side bars
  geom_col(position = "dodge", width = 0.7) +  
  
  scale_fill_manual(name = "Group", 
                    values = c("Interesting (A Group)" = "red", 
                               "Interesting (B Group)" = "blue", 
                               "Interesting (C Group)" = "green")) +
  
  # black and white theme
  theme_bw(base_size = 16) +
  
  # customize axis and label
  labs(x = "Interesting", y = "Score") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1, size = 8))

print(p_interesting)

```




