---
title: "R Notebook Sep25"
output: html_notebook
---
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

# After class assignment

```{r}
install.packages("dplyr")
```
```{r}
# Load necessary libraries
library(readxl)
library(dplyr)

# Load the Excel file
data <- read_excel("SOC681_Data_Kim.xlsx", sheet = "all")

# Group by 'grade group' and combine the reflections
combined_reflections <- data %>%
  group_by(`grade group`) %>%
  summarize(
    combined_confusing = paste(na.omit(`confusing reflection`), collapse = " "),
    combined_interesting = paste(na.omit(`interesting reflection`), collapse = " ")
  )

# Replace unwanted characters (’) with apostrophe (')
combined_reflections$combined_confusing <- gsub("’", "'", combined_reflections$combined_confusing)
combined_reflections$combined_interesting <- gsub("’", "'", combined_reflections$combined_interesting)

# Replace any remaining newline characters or unwanted special characters
combined_reflections$combined_confusing <- gsub("[\r\n]", " ", combined_reflections$combined_confusing)
combined_reflections$combined_interesting <- gsub("[\r\n]", " ", combined_reflections$combined_interesting)

# Ensure data types are character
combined_reflections$combined_confusing <- as.character(combined_reflections$combined_confusing)
combined_reflections$combined_interesting <- as.character(combined_reflections$combined_interesting)

# View the cleaned dataframe 
View(combined_reflections)

# Export to CSV with proper handling of quotes and special characters
write.csv(combined_reflections, "combined_reflections_clean.csv", row.names = FALSE, quote = TRUE, fileEncoding = "UTF-8")

#write_xlsx(combined_reflections, "combined_reflections_clean.xlsx")

```





# In-class practice

```{r}
duke_web_scrape <- "Duke Experts: A Trusted Source for Policymakers\n\n\t\t\t\t\t\t\t"
grepl("Experts", duke_web_scrape) # find specific words
gsub("\t|\n", "", duke_web_scrape) # replace specific words with other words (or blank == delete!) # | means or
```

```{r}
some_text <- 
  c("Friends", "don't", "let", "friends", "make", "wordclouds")

some_text[grep("^[F]", some_text)] # find words with capitalized F
```


# Escaping text Wrong way
```{r}
text_chunk <- c("[This Professor is not so Great]")
gsub("[", "", text_chunk) # R does recognize [] as a square bracket, not a text that should be replaced. 
```

# Escaping text Right way
```{r}
text_chunk <- c("[This Professor is not so Great]")
gsub("\\[|\\]", "", text_chunk) # \\ means escape
```

# Tokenization 
## There are built-in functions for lemmatization (walk, walked, walking)
## But you have to look into your data to see if the lemmatization were done well.


# Group activity 
# what kinds of dictionary available in R 
# e.g. polarity, emotion,

# Install pacakges 
```{r}
install.packages("tidytext")
install.packages("dplyr")
install.packages("ggplot2")
install.packages("tm")
```

# Install and Load Required Libraries


```{r}
library(dplyr)  # For data manipulation if needed
```

```{r}
install.packages("quanteda", dependencies=TRUE)
```

```{r}
library(quanteda)
```

```{r}
data <- read.csv(file = "text_data_before_analysis.csv")

head(data)
```
# Prepare Text Data
```{r}
data_clean <- data %>% filter(!is.na(essay) & essay != "")
```


# Create a Corpus
```{r}
# Create a corpus from the essay column
corpus <- corpus(data_clean$essay)

# View the corpus
summary(corpus)
```





