---
title: "Practice"
author: "Jiwon Kim"
date: "2024-10-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load necessary libraries
```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(readr)
```

# Step 1: Read data from the CSV file
```{r}
df_liwc <- read_csv("SOC681_reflection_scoresOnly.csv")

print(head(df_liwc)) # Check the structure and make sure it reads correctly
```
# Step 2: Transform data to long format
```{r}
df_long <- pivot_longer(df_liwc, cols = -Group, names_to = "Dictionary", values_to = "Score")
```

# Step 3: Calculate the difference between the highest and lowest scores for each category
```{r}
df_diff <- df_long %>%
  group_by(Dictionary) %>%
  summarize(Difference = max(Score) - min(Score)) %>%
  arrange(desc(Difference)) # Sort by the biggest difference
```

# Step 4: Merge the difference information back to the long dataset
```{r}
df_long <- df_long %>%
  left_join(df_diff, by = "Dictionary")
```

# Step 5: Plot the data, ordered by the size of the difference
```{r}
graph_1 <- ggplot(df_long, aes(x = reorder(Dictionary, -Difference), y = Score, fill = Group)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Comparison of LIWC Categories Across Groups",
       x = "LIWC Category (Ordered by Difference)",
       y = "Percentage Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 3.5)) # Reduce font size of x-axis labels


graph_1
```

# Including Plots

```{r pressure, echo=FALSE}
#plot(pressure) 
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
